---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(rcme)
library(tidyverse)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcme

<!-- badges: start -->
<!-- badges: end -->

The goal of rcme is to support the user

## Installation

You can install the development version of rcme from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alex-cernat/rcme")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rcme)
## basic example code
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r}
me.1ex <- rcme_ind(
  formula = "disorder ~ violent_crime + white_british + unemployment + median_age",
  data = crime_disorder,
  key_predictor = "violent_crime",
  S = c(0.31, 0.67, 1.0),
  R_sd = c(0.08, 0.10, 0.12),
  log_var = T) 

me.1ex
```


```{r}

me.2ex <- rcme_out(
  formula = "damage_crime ~ collective_efficacy + unemployment + white_british + median_age",
  data = crime_damage,
  key_predictor = "collective_efficacy",
  S = c(0.29, 0.85, 1.0),
  R_sd = c(0.08, 0.10, 0.12),
  D = c(-0.3, -0.2, -0.1, 0),
  log_var = T)

```


```{r}
rcme_sim_plot(me.2ex, ci = T, naive = T)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
